### 2017-11-10 Graduate - Introduction to Analysis I/Assignment 7/7-Homework20171108.tex
add 1/2

\smallskip
\textbf{Solution:}
\smallskip

\item  Problem 10, Chapter 6
\item  Problem 13, Chapter 6

>>>>

\smallskip
\textbf{Solution:}
\smallskip
Sufficiency. Suppose $m^*(E) = m > 0$. Since each point in $E$ belongs to infinitely many of the $I_k $, then there exists $N > 0$, s.t. 
$$
\bigcup_{k=1}^N I_k\supset E,
$$
otherwise there exists $x\in E$, for each $N$, $x\notin \bigcup\limits_{k=1}^N I_k $, and that means $x\notin \bigcup\limits_{k=1}^{\infty}I_k $, which leads to a contradiction. Suppose the smallest $N$ such that $E \subset \bigcup\limits_{k=1}^N I_k$ to be $N_1 $, then using the same method, there exists $N_2 > N_1 $, s.t. $E \subset \bigcup\limits_{k=N_1+1}^{N_2} I_k$. By inductively constructing such $N_j $, we get a sequence $\{N_j\}$, s.t. $E \subset \bigcup\limits_{k=N_j+1}^{N_{j+1}} I_k $. Then by the definition of outer measure and finite addivity for open sets, 
$$
m = m^*(E) \le m^*(\bigcup\limits_{k=N_j+1}^{N_{j+1}}I_k) = \sum_{k = N_j+1}^{N_{j+1}}m(I_k).
$$
Then for each $M > 0$,
$$
\sum_{k=1}^{\infty}m(I_k) > Mm, 
$$
which makes a contradiction with $\sum_{k=1}^{\infty}m(I_k) < \infty$. Then $m^*(E) = 0$.

Necessity.
% Sufficiency. First, we show $\{I_k\}$ is a Vitali cover of $E$. Otherwise, there exists $x\in E, ~\epsilon > 0$, s.t. for each $I_k $ for which $x\in I_k $, $m(I_k) > \epsilon$. Then
% $$\sum_{k=1}^{\infty}m(I_k) \ge \sum_{x\in I_k}m(I_k) \ge \sum\limits_{x\in I_k}\epsilon = \infty
% $$
% since $x$ belongs to infinity many of $I_k $. This makes a contradiction with the assumptions.

% By Problem 6.6 we know Vitali Covering Lemma holds for general nondegenerate intervals, then

\bigskip
\item  Problem 10, Chapter 6
\item  Problem 13, Chapter 6
